Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-07-14 article-models-ttinternal.tex
small changes

\begin{defn}
A weakening algebra in context $\Gamma$ is a pre-weakening algebra $\cftalg{A}$
in context $\Gamma$ for which the weakening $\cftwk{\cftalg{A}}$ is a
pre-weakening homomorphism as explained in \autoref{rmk:cftwk-prewk},
satisfying the two additional judgmental equalities
expressing that: (1) the diagram
\begin{equation}\label{diag:cftwk-cftextcurry}
\begin{tikzcd}[column sep=large]
\ctxwk
  {\ctxext{\cftalgf{\cftalg{A}}}{\cftalgf{\cftfamalg{\cftalg{A}}}}}
  {\cftfamalg{\cftalg{A}}}
  \ar{r}{\ctxwk{\cftalgf{\cftfamalg{\cftalg{A}}}}{\cftwk{\cftalg{A}}}}
  \ar{dr}[swap]{\jcomp{}{\cftfamext}{\cftwk{\cftalg{A}}}}
& \ctxwk{\cftalgf{\cftfamalg{\cftalg{A}}}}{\cftfamalg{\cftfamalg{\cftalg{A}}}}
  \ar{d}{\jcomp{}{\cftctxext}{\cftwk{\cftalg{A}}}}
  \\
& \cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}
\end{tikzcd}
\end{equation}
and (2) that
\begin{equation}\label{eq:cftwk-cftempcurry}
\jhomeq
  { {\Gamma}{\cftalgc{\cftalg{A}}}
    }
  { \cftfamalg{\cftalg{A}}
    }
  { \cftfamalg{\cftalg{A}}
    }
  { \subst{\cftempf{\cftalg{A}}}{\cftwk{\cftalg{A}}}
    }
  { \cftidhom{\cftfamalg{\cftalg{A}}}
    }
\end{equation}
\end{defn}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Projection algebras}
Projection algebras will be weakening algebras with additional terms implementing
the identity terms. We call these algebras projection algebras because the
identity terms can only be formulated in weakening algebras and together with
weakening, the identity terms provide for all the projections. In a weakening
algebra $\cftalg{A}$ in context $\Gamma$, identity terms are implemented by a term
\begin{equation*}
\jterm
  { { {\Gamma}
      {\cftalgc{\cftalg{A}}}
      }
    { \cftalgf{\cftalg{A}}
      }
    }
  {\subst{{\idtm{\cftalgf{\cftalg{A}}}}{\cftwkc{\cftalg{A}}}}{\cftalgt{\cftfamalg{\cftalg{A}}}}}
  {\cftidtm{\cftalg{A}}}
\end{equation*}
We will require additionally that identity terms are compatible with weakening,
i.e.~an abstraction of the rule stated in \autoref{comp-wi}. Since this is the
only additional rule for projection algebras, we immediately state the 
definition.

\begin{defn}
A \emph{projection algebra $\cftalg{A}$ in context $\Gamma$} is a weakening algebra
$\cftalg{A}$ in context $\Gamma$ together with a term
\begin{equation*}
\jterm
  { { {\Gamma}
      {\cftalgc{\cftalg{A}}}
      }
    { \cftalgf{\cftalg{A}}
      }
    }
  {\subst{{\idtm{\cftalgf{\cftalg{A}}}}{\cftwkc{\cftalg{A}}}}{\cftalgt{\cftfamalg{\cftalg{A}}}}}
  {\cftidtm{\cftalg{A}}}
\end{equation*}
satisfying the judgmental equality
\begin{align*}
& \subst
  { \ctxwk
      { \cftalgf{\cftalg{A}}}
      { \jcomp
        { }
        { \cftctxext}
        { \cftidtm{\cftalg{A}}
          }
        }
    }
  { { \ctxwk
        { \cftalgf{\cftalg{A}}}
        { \subst { \idtm
            { \jcomp
                { }
                { \cftctxext}
                { \cftalgf{\cftalg{A}}
                  }
              }
          }
          { \jcomp
              { }
              { \cftctxext
                }
              { \cftwkc{\cftalg{A}}
                }
            }
          }
      }
    { \jcomp
        { }
        { \ctxwk{\cftalgf{\cftalg{A}}}{\cftfamext}}
        { \cftwkt{\cftalg{A}}}
      }
    }
  \\
& \jdeq
  \jcomp{}
    { \cftwkf{\cftalg{A}}}
    { \jcomp{}
        { \cftwkc{\cftalg{A}}}
        { \jcomp{}
            { \cftctxext}
            { \jcomp{}
              { \cftctxext}
              { \cftidtm{\cftalg{A}}}
              }
          }
      }
\end{align*}
of terms of %
$ \jcomp{}
    { \cftwkf{\cftalg{A}}}
    { \jcomp{}
        { \cftwkc{\cftalg{A}}}
        { \jcomp{}
            { \cftctxext}
            { \jcomp{}
              { \cftctxext}
              { \subst
                  { {\idtm{\cftalgf{\cftalg{A}}}}
                    {\cftwkc{\cftalg{A}}}
                    }
                  { \cftalgt{\cftfamalg{\cftalg{A}}}
                    }
                }
              }
          }
      }$
in context \ldots.

The term $\cftidtm{\cftalg{A}}$ of a projection algebra $\cftalg{A}$ in context
$\Gamma$ is called the \emph{internal identity term of $\cftalg{A}$}.
\end{defn}

\begin{rmk}
We shall have to verify that the condition on the internal identity term 
$\cftidtm{\cftalg{A}}$ of a projection algebra $\cftalg{A}$ in context $\Gamma$
is indeed well-typed. More precisely, we have to demonstrate that the judgmental
equality
\begin{align*}
& \jdeq
  \jcomp{}
    { \cftwkf{\cftalg{A}}}
    { \jcomp{}
        { \cftwkc{\cftalg{A}}}
        { \jcomp{}
            { \cftctxext}
            { \jcomp{}
              { \cftctxext}
              { \subst
                  { {\idtm{\cftalgf{\cftalg{A}}}}
                    {\cftwkc{\cftalg{A}}}
                    }
                  { \cftalgt{\cftfamalg{\cftalg{A}}}
                    }
                }
              }
          }
      }  
\end{align*}
of families in context \ldots holds.
\end{rmk}

\begin{thm}
Suppose $\cftalg{A}$ is a projection algebra in context $\Gamma$. Then
$\cftfamalg{\cftalg{A}}$ with the internal identity term
\begin{equation*}
\cftidtm{\cftfamalg{\cftalg{A}}}\defeq\jcomp{}{\cftctxext}{\cftidtm{\cftalg{A}}}
\end{equation*}
is a projection algebra in context $\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$.
\end{thm}

\begin{thm}
Suppose $\cftalg{Q}$ is a projection algebra in context $\ctxext{\Gamma}{B}$ and
let $\jfam{\Gamma}{A}$. Then $\ctxwk{A}{\cftalg{Q}}$ together with the
internal identity term
\begin{equation*}
\cftidtm{\ctxwk{A}{\cftalg{Q}}}\defeq \ctxwk{A}\cftidtm{\cftalg{Q}}
\end{equation*}
is a projection algebra in context $\ctxext{{\Gamma}{A}}{B}$.
\end{thm}

\begin{thm}
Suppose $\cftalg{Q}$ is a projection algebra in context $\ctxext{{\Gamma}{A}}{P}$
and let $\jterm{\Gamma}{A}{x}$. Then $\subst{x}{\cftalg{Q}}$ together with the
internal identity term
\begin{equation*}
\cftidtm{\subst{x}{\cftalg{Q}}} \defeq \subst{x}{\cftidtm{\cftalg{Q}}}
\end{equation*}
is a projection algebra in context $\ctxext{\Gamma}{\subst{x}{P}}$.
\end{thm}

@@

\begin{lem}
Let $\cftalg{A}$ be a substitution algebra in context $\Gamma$. Then we have the
judgmental equality
\begin{align*}
& \jcomp{}
    { \apply\cftsubst{\cftalg{A}}%
      { \apply\cftctxext%
          { \apply\cftctxext{\gamma}{a}}{p}
        }
      { q}
      { g}
      }
    { \subst
        { q}
        { { p}
          { \cftfamhom{\apply\cftsubst{\cftalg{A}}{\gamma}{a}{x}}}
          }
      }
  \\
& \jdeq
\end{align*}
of CFT-homomorphisms from ... to ... in context $\Gamma$,
for $\gamma:A$, $a:\subst{\gamma}{\cftalgf{\cftalg{A}}}$, 
$x:\subst{a}{{\gamma}{\cftalgt{\cftalg{A}}}}$,
$p:\subst{\apply\cftctxext{\gamma}{a}}{\cftalgf{\cftalg{A}}}$
$q:\subst{\apply\cftctxext{\apply\cftctxext{\gamma}{a}}{p}}{\cftalgf{\cftalg{A}}}$
and $g:\subst{\apply\cftctxext{\apply\cftctxext{\apply\cftctxext{\gamma}{a}}{p}}{q}}{\cftalgt{\cftalg{A}}}$
\end{lem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{E-algebras}
E-algebras will be CFT-algebras with a weakening operation, identity terms and
a substitution operation making it a projection algebra and a substitution 
algebra at the same time. Additionally the weakening operation, identity terms
and the substitution operation are all required to be compatible with each
other. Thus, we need to require the abstractions of the rules stated in
\autoref{comp-sw,comp-ws,cancellation-ws,comp-si,cancellation-i}.

>>>>

\begin{defn}
A weakening algebra in context $\Gamma$ is a pre-weakening algebra $\cftalg{A}$
in context $\Gamma$ for which the weakening $\cftwk{\cftalg{A}}$ is a
pre-weakening homomorphism as explained in \autoref{rmk:cftwk-prewk},
satisfying the two additional judgmental equalities
expressing that: (1) the diagram
\begin{equation}\label{diag:cftwk-cftextcurry}
\begin{tikzcd}[column sep=large]
\ctxwk
  {\ctxext{\cftalgf{\cftalg{A}}}{\cftalgf{\cftfamalg{\cftalg{A}}}}}
  {\cftfamalg{\cftalg{A}}}
  \ar{r}{\ctxwk{\cftalgf{\cftfamalg{\cftalg{A}}}}{\cftwk{\cftalg{A}}}}
  \ar{dr}[swap]{\jcomp{}{\cftfamext}{\cftwk{\cftalg{A}}}}
& \ctxwk{\cftalgf{\cftfamalg{\cftalg{A}}}}{\cftfamalg{\cftfamalg{\cftalg{A}}}}
  \ar{d}{\jcomp{}{\cftctxext}{\cftwk{\cftalg{A}}}}
  \\
& \cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}
\end{tikzcd}
\end{equation}
of pre-weakening algebras in context $\ctxext{{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}{\cftalgf{\cftfamalg{\cftalg{A}}}}$ commutes judgmentally and (2) that
\begin{equation}\label{eq:cftwk-cftempcurry}
\jhomeq
  { {\Gamma}{\cftalgc{\cftalg{A}}}
    }
  { \cftfamalg{\cftalg{A}}
    }
  { \cftfamalg{\cftalg{A}}
    }
  { \subst{\cftempf{\cftalg{A}}}{\cftwk{\cftalg{A}}}
    }
  { \cftidhom{\cftfamalg{\cftalg{A}}}
    }
\end{equation}
\end{defn}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Projection algebras}
Projection algebras will be weakening algebras with additional terms implementing
the identity terms. We call these algebras projection algebras because the
identity terms can only be formulated in weakening algebras and together with
weakening, the identity terms provide for all the projections.

\begin{defn}
A \emph{pre-projection algebra $\cftalg{A}$ in context $\Gamma$} consists of a 
weakening algebra $\cftalg{A}$ in context $\Gamma$ together with an 
\emph{internal identity term}
\begin{equation*}
\jterm
  { { {\Gamma}
      {\cftalgc{\cftalg{A}}}
      }
    { \cftalgf{\cftalg{A}}
      }
    }
  {\subst{{\idtm{\cftalgf{\cftalg{A}}}}{\cftwkc{\cftalg{A}}}}{\cftalgt{\cftfamalg{\cftalg{A}}}}}
  {\cftidtm{\cftalg{A}}}.
\end{equation*}
\end{defn}

\begin{defn}
Suppose $\cftalg{A}$ is a pre-projection algebra in context $\Gamma$. Then we
define the pre-projection algebra $\cftfamalg{\cftalg{A}}$ in context 
$\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$ by taking
\begin{equation*}
\cftidtm{\cftfamalg{\cftalg{A}}}
  \defeq \jcomp{}{\cftctxext}{\cftidtm{\cftalg{A}}}.
\end{equation*}
\end{defn}

\begin{defn}
Suppose $\cftalg{Q}$ is a pre-projection algebra in context $\ctxext{\Gamma}{B}$ and
let $\jfam{\Gamma}{A}$. Then we define the pre-projection algebra 
$\ctxwk{A}{\cftalg{Q}}$ in context $\ctxext{{\Gamma}{A}}{\ctxwk{A}{B}}$ by 
taking
\begin{equation*}
\cftidtm{\ctxwk{A}{\cftalg{Q}}}\defeq \ctxwk{A}\cftidtm{\cftalg{Q}}.
\end{equation*}
\end{defn}

\begin{defn}
Suppose $\cftalg{Q}$ is a pre-projection algebra in context $\ctxext{{\Gamma}{A}}{P}$
and let $\jterm{\Gamma}{A}{x}$. Then we define the pre-projection algebra 
$\subst{x}{\cftalg{Q}}$ in context $\ctxext{\Gamma}{\subst{x}{P}}$ by taking
\begin{equation*}
\cftidtm{\subst{x}{\cftalg{Q}}} \defeq \subst{x}{\cftidtm{\cftalg{Q}}}.
\end{equation*}
\end{defn}

\begin{defn}
A pre-projection homomorphism from $\cftalg{A}$ to $\cftalg{B}$ in context
$\Gamma$ is a weakening homomorphism $\cfthom{f}$ from $\cftalg{A}$ to
$\cftalg{B}$ in context $\Gamma$ for which the diagram
\begin{equation*}
\begin{tikzcd}[column sep=10em]
\subst
  {{\idtm{\cftalgf{\cftalg{A}}}}{\cftwkc{\cftalg{A}}}}
  {\cftalgt{\cftfamalg{\cftalg{A}}}}
  \ar{r}{\subst{{\idtm{\cftalgf{\cftalg{A}}}}{\cftwkc{\cftalg{A}}}}{\cfthomt{\cftfamhom{\cfthom{f}}}}}
  \ar[fib,xshift=-.7ex]{d}
  &
\subst
  {{\idtm{\cftalgf{\cftalg{B}}}}{\cftwkc{\cftalg{B}}}}
  {\cftalgt{\cftfamalg{\cftalg{B}}}}
  \ar[fib,xshift=-.7ex]{d}
  \\
\cftalgf{\cftalg{A}}
  \ar{r}[swap]{\cfthomf{\cfthom{f}}}
  \ar[fib]{d}
  \ar[densely dotted,xshift=.7ex]{u}[swap]{\cftidtm{\cftalg{A}}}
  &
\cftalgf{\cftalg{B}}
  \ar[fib]{d}
  \ar[densely dotted,xshift=.7ex]{u}[swap]{\cftidtm{\cftalg{B}}}
  \\
\cftalgc{\cftalg{A}}
  \ar{r}[swap]{\cfthomc{\cfthom{f}}}
  &
\cftalgc{\cftalg{B}}
\end{tikzcd}
\end{equation*}
\end{defn}

\begin{defn}
A projection algebra in context $\Gamma$ is a pre-projection algebra in context
$\Gamma$ for which weakening is a pre-projection homomorphism.
\end{defn}

\begin{defn}
A projection homomorphism is a pre-projection homomorphism between projection
algebras.
\end{defn}

\begin{thm}
Suppose $\cftalg{A}$ is a projection algebra in context $\Gamma$. Then the 
pre-projection algebra $\cftfamalg{\cftalg{A}}$ is a projection algebra in context 
$\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$.
\end{thm}

\begin{thm}
Suppose $\cftalg{Q}$ is a projection algebra in context $\ctxext{\Gamma}{B}$ and
let $\jfam{\Gamma}{A}$. Then the pre-projection algebra 
$\ctxwk{A}{\cftalg{Q}}$ is a
projection algebra in context $\ctxext{{\Gamma}{A}}{\ctxwk{A}{B}}$.
\end{thm}

\begin{thm}
Suppose $\cftalg{Q}$ is a projection algebra in context $\ctxext{{\Gamma}{A}}{P}$
and let $\jterm{\Gamma}{A}{x}$. Then the pre-projection algebra 
$\subst{x}{\cftalg{Q}}$ is a
projection algebra in context $\ctxext{\Gamma}{\subst{x}{P}}$.
\end{thm}

\begin{cor}
In a projection algebra $\cftalg{A}$ in context $\Gamma$, weakening is a
projection homomorphism.
\end{cor}

@@

\begin{thm}
Suppose $\cftalg{A}$ is a substitution algebra in context $\Gamma$. Then
the pre-substitution algebra $\cftfamalg{\cftalg{A}}$ is a substitution algebra
in context 
$\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$.
\end{thm}

\begin{thm}
Suppose $\cftalg{Q}$ is a substitution algebra in context $\ctxext{\Gamma}{B}$ 
and let $\jfam{\Gamma}{A}$. Then the pre-substitution algebra 
$\ctxwk{A}{\cftalg{Q}}$ is a substitution algebra in context 
$\ctxext{{\Gamma}{A}}{\ctxwk{A}{B}}$.
\end{thm}

\begin{thm}
Suppose $\cftalg{Q}$ is a substitution algebra in context $\ctxext{{\Gamma}{A}}{P}$
and let $\jterm{\Gamma}{A}{x}$. Then the pre-substitution algebra 
$\subst{x}{\cftalg{Q}}$ is a substitution algebra in context 
$\ctxext{\Gamma}{\subst{x}{P}}$.
\end{thm}

\begin{cor}
In a substitution algebra $\cftalg{A}$ in context $\Gamma$, substitution is a
substitution homomorphism.
\end{cor}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{E-algebras}
\begin{defn}
A CFT-algebra $\cftalg{A}$ in context $\Gamma$ with internal weakening, identity terms and
substitution
\begin{align*}
\jalign\jhom
  {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
  {\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
  {\cftfamalg{\cftfamalg{\cftalg{A}}}}
  {\cftwk{\cftalg{A}}}
  \\
\jalign\jterm
  { { {\Gamma}
      {\cftalgc{\cftalg{A}}}
      }
    { \cftalgf{\cftalg{A}}
      }
    }
  {\subst{{\idtm{\cftalgf{\cftalg{A}}}}{\cftwkc{\cftalg{A}}}}{\cftalgt{\cftfamalg{\cftalg{A}}}}}
  {\cftidtm{\cftalg{A}}}
  \\
\jalign\jhom
  {{{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}{\cftalgt{\cftalg{A}}}}
  {\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}
  {\ctxwk{\cftalgt{\cftalg{A}}}{{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  {\cftsubst{\cftalg{A}}}
\end{align*}
is said to be an \emph{E-algebra in context $\Gamma$} if both weakening and substitution are both
projection and substitution homomorphisms and if (1) the diagram
\begin{equation*}
\begin{tikzcd}[column sep=large]
\ctxwk
  { \cftalgt{\cftalg{A}}}
  { { \cftalgf{\cftalg{A}}}
    { \cftfamalg{\cftalg{A}}}
    }
  \ar{r}{\ctxwk{\cftalgt{\cftalg{A}}}{\cftwk{\cftalg{A}}}}
  \ar{dr}[swap]{\cftidhom{}}
  &
\ctxwk
  { \cftalgt{\cftalg{A}}}
  { \cftfamalg{\cftfamalg{\cftalg{A}}}}
  \ar{d}{\cftsubst{\cftalg{A}}}
  \\
  &
\ctxwk
  { \cftalgt{\cftalg{A}}}
  { { \cftalgf{\cftalg{A}}}
    { \cftfamalg{\cftalg{A}}}
    }
\end{tikzcd}
\end{equation*}
of CFT-algebras in context 
$\ctxext{{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}{\cftalgt{\cftalg{A}}}$
commutes judgmentally
and (2) the diagram
\begin{equation*}
\begin{tikzcd}[column sep=large]
\cftfamalg{\cftfamalg{\cftalg{A}}}
  \ar{r}{\subst{\idtm{\cftalgf{\cftalg{A}}}}{\cftfamhom{\cftwk{\cftalg{A}}}}}
  \ar{dr}[swap]{\cftidhom{}}
  &
\subst
  { \idtm{\cftalgf{\cftalg{A}}}}
  { \jcomp{}
      { \cftwk{\cftalg{A}}}
      { \cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}}
    }
  \ar{d}
    { \subst
        { \cftidtm{\cftalg{A}}}
        { { { \idtm{\cftalgf{\cftalg{A}}}}
            { \cftwkc{\cftalg{A}}}
            }
          { \cftsubst{\cftalgf{\cftalg{A}}}}
          }
      }
  \\
  &
    { \subst
        { \cftidtm{\cftalg{A}}}
        { { { \idtm{\cftalgf{\cftalg{A}}}}
            { \cftwkc{\cftalg{A}}}
            }
          { \ctxwk
              { \cftalgt{\cftfamalg{\cftalg{A}}}}
              { { \cftalgf{\cftfamalg{\cftalg{A}}}}
                { \cftfamalg{\cftfamalg{\cftalg{A}}}}
                }
            }
          }
      }
\end{tikzcd}
\end{equation*}
of CFT-algebras in context 
$\ctxext{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}$ commutes
judgmentally.

E-algebras are considered judgmentally equal if their underlying CFT-algebras
and their internal weakening, identity terms and substitution are judgmentally
equal.
\end{defn}

\begin{thm}
Suppose $\cftalg{A}$ is an E-algebra in context $\Gamma$. Then
$\cftfamalg{\cftalg{A}}$ is an E-algebra in context $\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$.
\end{thm}

\begin{thm}
Suppose $\cftalg{Q}$ is an E-algebra in context $\ctxext{\Gamma}{B}$ and that
$\jfam{\Gamma}{A}$. Then $\ctxwk{A}{\cftalg{Q}}$ is an E-algebra in context
$\ctxext{{\Gamma}{A}}{\ctxwk{A}{B}}$. 
\end{thm}

\begin{thm}
Suppose $\cftalg{Q}$ is an E-algebra in context $\ctxext{{\Gamma}{A}}{P}$ and
that $\jterm{\Gamma}{A}{x}$. Then $\subst{x}{\cftalg{Q}}$ is an E-algebra in
context $\ctxext{\Gamma}{\subst{x}{P}}$.
\end{thm}

\begin{thm}
Suppose $\cftalg{Q}$ is an E-algebra in context $\ctxext{\Gamma}{B}$ and that
$\jfam{\Gamma}{A}$. Then we have the
judgmental equality $\cftfamalg{\ctxwk{A}{\cftalg{Q}}}\jdeq\ctxwk{A}{\cftfamalg{\cftalg{Q}}}$
of E-algebras in context $\ctxext{{{\Gamma}{A}}{\ctxwk{A}{B}}}{\ctxwk{A}{\cftalgc{\cftalg{Q}}}}$.
\end{thm}

\begin{thm}
Suppose $\cftalg{Q}$ is an E-algebra in context $\ctxext{{\Gamma}{A}}{P}$ and
that $\jterm{\Gamma}{A}{x}$. Then we have the judgmental equality
$\cftfamalg{\subst{x}{\cftalg{Q}}}\jdeq\subst{x}{\cftfamalg{\cftalg{Q}}}$
of E-algebras in context $\ctxext{{\Gamma}{\subst{x}{P}}}{\subst{x}{\cftalgc{\cftalg{Q}}}}$.
\end{thm}
